Discovery of s-process stars in the LAMOST survey

### 2018-02-06 article/ms.tex
add acks
typo
add fig3

\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A.~R. Casey,$^{1,2}$
M.~T. Miles,$^{1}$
A.~J. Kemp,$^{1}$ 
A.~I. Karakas,$^{1}$\newauthor
A.~Y.~Q. Ho,$^{3}$
J.~C. Lattanzio,$^{1}$
K.~C. Schlaufman,$^{4}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{4}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{basrtest4.png}
    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr]; y-axis) for 257 Barium star candidates. \todo{Add Cristillo yields}}
    \label{fig:figure3}
\end{figure}

@@

\section*{Acknowledgements}
We thank Alex Ji (Carnegie Observatories) for useful discussions.
A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences. 
This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.

>>>>

\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A.~R. Casey,$^{1,2}$
M.~T. Miles,$^{1}$
A.~J. Kemp,$^{1}$ 
A.~I. Karakas,$^{1}$\newauthor
A.~Y.~Q. Ho,$^{3}$
J.~C. Lattanzio,$^{1}$ and
K.~C. Schlaufman$^{4}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{4}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{yields.pdf}
    \caption{Metallicities ([Fe/H]; x-axis) and heavy-to-light s-process abundance ratios ([hs/ls], taken as [Ba/Sr] as measured from LAMOST; y-axis) for 257 Barium star candidates. Coloured lines indicate surface [hs/ls] yields from \citet{cristallo2015} for different masses.}
    \label{fig:figure3}
\end{figure}

@@

\section*{Acknowledgements}
We thank Alex Ji (Carnegie Observatories), David W. Hogg (NYU), Melissa Ness (Columbia), and Hans-Walter Rix (MPIA) for useful discussions. 
A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences. 
This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.
